\section{Installation of FADA toolkit}
FADA toolkit compilation requires two libraries:
\begin{description}
 \item[piplib:] FADA toolkit works with the version 1.3.6, accessible here  \cite{piplib_website}.
 \item[BGL:] the Boost Graph Library (we tested the version 1.39.0). You can get it here \begin{footnotesize}\verb|http://www.boost.org/| \end{footnotesize}
 \end{description}
Unlike \verb|piplib|, \verb|BGL| is a header-only library. No installation is required for BGL. \verb|piplib| have to be previously installed.

FADA toolkit sources can be downloaded from \cite{fadalib_website}. Unpack it into a directory \verb|$FADA_ROOT|. Usual installation commands are :
\begin{verbatim}
$ cd $FADA_ROOT
$ ./configure
$ make
\end{verbatim}

and optionally 

\begin{verbatim}
$ make install
\end{verbatim}


The configure script checks for \verb|libpiplib64.so| and \verb|BGL| headers, and may not be able to find it if its installation was redirected to non standard directories. In this case, you need to run the \verb|./configure| script with the \verb|--with-pip-lib|, \verb|--with-pip-inlcude| and \verb|--with-boost|  options:

\begin{footnotesize}
\begin{verbatim}

$ ./configure --with-pip-lib=PIP_LIB_DIR   --with-pip-include=PIP_INCLUDE_DIR
              --with-boost=BOOST_DIR

\end{verbatim}
\end{footnotesize}

You can test the installation by doing:

\begin{verbatim}

$ cd $FADA_ROOT/examples/tests
$ make test

\end{verbatim}

\subsection{FADA Software Prerequisites Summary}
\label{fada_prerequis}
\begin{enumerate}
\item You may have to add the path of \verb|libpiplib64.so| into the variable \verb|LD_LIBRARY_PATH|.
 \item \verb|FADAtool| uses \verb|gcc| to preprocess inputfiles ( \verb|-E| option). \verb|gcc| is required.
 \item You may also need a web browser to explore HTML pages and view pictures produced by our tool. The default browser is \verb|firefox|.
 \item You may also need to install \textbf{GraphViz} tool suites (especially \verb|dot|) and \verb|latex2html| : these tools are necessary to convert \verb|.dot| and \verb|.tex| files produced by FADA toolkit to \verb|.png| pictures and \verb|.html| pages.
 \item FADAtool can produce \verb|.vcg| graphs, you may need a vcgviewer to visualize our output (here a good software \begin{small}\verb|http://code.google.com/p/vcgviewer/|                                                                                                                       \end{small}).
\end{enumerate}


% If you want to use \verb|FADAtool| for producing HTML outputs, you would also need to install the \verb|GraphViz| toolsuites (especially \verb|dot|) and \verb|latex2html|: these tools are necessary to convert \verb|.dot| and \verb|.tex| files produced by FADA toolkit to \verb|.png| pictures and \verb|.html| pages. \verb|FADAtool| needs also \verb|gcc| to be installed in order to preprocess input files.
% 
